---
title: "Scientific Accountability in Shiny Apps"
subtitle: "Generating reproducible reports with Shiny apps"
author: 
  - name: "January Weiner"
    orcid: 0000-0003-1438-7819
    affiliations:
     - ref: cubi
affiliations:
  - id: cubi
    name: Core Unit for Bioinformatics, BIH@Charité
    address: Charitéplatz 1, 
    postal-code: 10117 
    city: Berlin 
    country: Germany
title-slide-attributes:
  data-background-image: files/title_background.svg
format:
  revealjs:
    footer: "Core Unit for Bioinformatics, BIH@Charite"
    theme: cubi.scss
    logo: files/BIH_logo_whiteBG.svg
    transition: fade
    slide-number: true
    smaller: true
    navigation-mode: linear
    self-contained: true
---


## Reproducibility vs Accountability

::: {.aside}
In practice, what is reproducible, is not accountable.
:::

## The CUBI environment

## Customization

 * Check the `files` folder for alternate background images and logos.
 * Some of the changes you can make directly in this qmd file
 * Others require you to edit the `cubi.scss` file.

For example, to make the title slide with white background, you can use the
`files/title_background_white.svg` file, but you will also have to change
the `title`, `subtitle` and `quarto-title-author` colors in the `cubi.scss`
file, otherwise they will stay white.

## Multicolumn slide

:::: {.columns}

::: {.column width="40%" .fragment}
### Left column title

Left column...
:::

::: {.column width="60%" .fragment}
### Right column title

Right column (60%)...

(adding `.fragment` causes the contents to be displayed in steps)
:::

::::



# Part II separator slide {.inverse background-image="files/divider_slide_bg.svg"}

## Simple numbered and unnumbered lists

:::: {.columns}

::: {.column width="50%"}
 * One
 * Two
:::

::: {.column width="50%"}
 1. One
 2. Two
:::

::::

## Incremental list

::: {.incremental}
 - Item 1
 - Item 2
 - Item 3
:::


## Incremental contents

First part

. . .

Second part


---

This is a slide without a title (use the dashes to separate)

## Transitions {transition="zoom"}

Define them in the YAML header or like here, in the slide title.

Types: none, fade, slide, convex, concave, zoom


## Code 


```{r}
#| echo: true
#| output-location: column-fragment
#| label: fig-sample
#| fig-cap: A dumb plot
plot(1:10)
```

::: {.callout-tip}
Ctrl-click on the image to zoom. And here is a `r pi` for you.
:::

## Code

There are many customization options for the code. For example, you can
highlight (and even animate) certain lines of code:


```{r}
#| code-line-numbers: "|1|2|3|"
#| echo: true
a <- rnorm(10)
b <- rnorm(10) + a
c <- a + b * rnorm(10)
```

You can also specify where precisely should the output of the code go:
below the code (default), on the next slide, on a right-hand column...




## Thank you {.inverse}

:::: {.columns}

::: {.column width="40%"}
Acknowledgements

 - N.N.
 - Y.Y.
 
:::

::: {.column width="40%"}
Sources

 - Source 1
 - Source 2
:::

::: {.column width="20%"}

```{r}
#| fig-width: 5
#| fig-height: 5
library(qrcode)
plot(qr_code("https://google.com"))
```



:::


::::
